---
title: "R Notebook"
output: html_notebook
---

### Given a dictionary consisting of many roots and a sentence, stem all the words in the sentence with the root forming it.

Stemming is commonly used in text and sentiment analysis. In this question, you will write a Python function that will convert certain words from the list to their root form - Interview Query.

#### Input:

The function will take two arguments: list of root words and sentence.  


roots = ["cat", "bat", "rat"]
sentence = "the cattle was rattled by the battery"
 
#### Output:

It will return the sentence with root words. 


"the cat was rat by the bat"

```{r}
stem_sentence <- function(roots, sentence) {
  # Step 1: Split the sentence into words
  words <- unlist(strsplit(sentence, " "))
  
  # Step 2: Replace words in the sentence with their roots
  for (i in 1:length(words)) {
    for (root in roots) {
      if (startsWith(words[i], root)) {
        words[i] <- root
        break  # Once a root is found, no need to check further roots
      }
    }
  }
  
  # Step 3: Reconstruct the sentence
  return(paste(words, collapse = " "))
}

# Test the function
roots <- c("cat", "bat", "rat")
sentence <- "the cattle was rattled by the battery"
result <- stem_sentence(roots, sentence)
print(result)  # Output: "the cat was rat by the bat"

```

```{r}
# Function to check if a string is a palindrome
is_palindrome <- function(text) {
  
  # Step 1: Convert the string to lowercase
  text <- tolower(text)
  
  # Step 2: Clean the string by removing non-alphanumeric characters
  text <- gsub("\\W+", "", text)
  
  # Step 3: Reverse the cleaned string
  rev_text <- paste(rev(strsplit(text, NULL)[[1]]), collapse = "")
  
  # Step 4: Compare the original cleaned string with the reversed string
  return(text == rev_text)
}

# Step 5: Create a list of test strings
List <- c('Anna', '**Radar****','Abid','(Level)', 'Data')

# Step 6: Loop through the list and check each string
for (text in List) {
  # Print the result for each string
  print(paste("Is", text, "a palindrome?", is_palindrome(text)))
}

```


