---
title: "R Notebook"
output: html_notebook
---

### R Basics and Data Structures

#### 1. **Review R Syntax, Data Types, and Structures**

**R Syntax Basics:**

-   **Variables and Assignments:**

```{r}
x <- 5

y <- "Hello, R!"

z <- TRUE

```

-   **Basic Arithmetic Operations:**

```{r}
add <- 10+5

diff <- 10-5

prod <- 10*5

quot <- 10/5

vec1 <- c(1,2,3,4)
vec2 <- c(4,5,6)

vec_sum <- vec1 + vec2
vec_diff <- vec2 - vec1
vec_prod <- vec2 * vec1

vec_quot <- vec2 / vec1

vec_sum
vec_diff
vec_prod
vec_quot


```
-   **Advanced Arithmetic Operations:**

```{r}
e <- 3
f <- 4
product <- e * f  # product is 12

mat1 <- matrix(1:4, nrow = 2)
mat2 <- matrix(4:1, nrow = 2)
mat_prod <- mat1 %*% mat2  # Matrix multiplication
g <- 25
h <- 5
quotient <- g / h  # quotient is 5
vec_quotient <- vec1 / vec2  # vec_quotient is c(0.25, 0.4, 0.5)

i <- 2
j <- 3
power_result <- i ^ j  # power_result is 8 (2^3)
vec_power <- vec1 ^ 2  # vec_power is c(1, 4, 9)


```

```{r}
k <- 10
l <- 3
remainder <- k %% l  # remainder is 1 (10 %% 3)

vec_modulus <- vec1 %% 2  # vec_modulus is c(1, 0, 1)

m <- 10
n <- 3
int_div <- m %/% n  # int_div is 3 (10 %/% 3)

vec_int_div <- vec1 %/% 2  # vec_int_div is c(0, 1, 1)


```

```{r}
o <- -15
abs_value <- abs(o)  # abs_value is 15

vec_abs <- abs(c(-1, -2, -3))  # vec_abs is c(1, 2, 3)

```


```{r}
p <- 16
sqrt_value <- sqrt(p)  # sqrt_value is 4

vec_sqrt <- sqrt(c(4, 9, 16))  # vec_sqrt is c(2, 3, 4)
```

```{r}
numbers <- c(1, 2, 3, 4, 5)
mean_value <- mean(numbers)  # mean_value is 3
sd_value <- sd(numbers)  # sd_value is approximately 1.581
```


```{r}
max_value <- max(numbers)  # max_value is 5
min_value <- min(numbers)  # min_value is 1
```


**Data Types:**

-   **Numeric:**

```{r}
num <- 42.5
```


-   **Character:**

```{r}
char <- "This is R programming"
```


-   **Logical:**

```{r}
bool <- TRUE
bool2 < FALSE
```


-   **Factor:**

```{r}
factor_var <- factor(c("Male", "Female", "Female", "Male", "Female"))

factor_var
```



**Data Structures:**

-   **Vectors:**
    
```{r}
vec <- c(1,2,3,4,5)
char_vec <- c("a", "b", "c")

vec
char_vec

```


-   **Lists:**

```{r}
list1 <- list(name = c("John", "Makima"), age = 25, scores = c(90,85,88))

list1
```


-   **Data Frames:**
    
```{r}
df <- data.frame(name = c("Alice", "Bob", "Charlie"), age =c(25,30,35))

df
```

    
-   **Matrices:**

```{r}
matrice1 <- matrix(1:9, nrow = 3, ncol =  3)
matrice2 <- matrix(1:16, ncol = 4, nrow =  4)
matrice3 <- matrix(1:15, ncol = 4, nrow =  4)

matrice1
matrice2
matrice3

```


#### 2. **Practice Writing Functions and Using Control Structures**

**Writing Functions:**

-   **Simple Function:**   

```{r}
addition <- function(a, b) {
  return(a+b)
}

addition(3, 12)

result <- addition(10, 30)

result
```

  
**Control Structures:**

-   **If-Else:**

```{r}
num <- 10

if (num > 0) {
  print("positive number")
}else {
  print("Negative number")
}


```

    
-   **For Loop:**
    
```{r}
for (i in 1:5) {
  print(i)
}
```

    
-   **While Loop:**
    
```{r}
counter <- 1

while (counter <= 5) {
  print(counter)
  counter <- counter + 1
}
```


### 3. **LeetCode Question: Two Sum (Easy)**

**Problem Statement:**

Given an array of integers `nums` and an integer `target`, return the indices of the two numbers such that they add up to `target`.

You may assume that each input would have exactly one solution, and you may not use the same element twice.


```{r}
two_sum_all_pairs <- function(nums, target) {
  # Initialize an empty list to store the pairs
  result_pairs <- list()
  
  # Iterate through each element in nums
  for (i in seq_along(nums)) {
    
    # For each element, check the remaining elements
    for (j in (i + 1):length(nums)) {
      
      # Check for NA values and skip them
      if (is.na(nums[i]) || is.na(nums[j])) {
        next
      }
      
      # Check if the sum of the two elements equals the target
      if (nums[i] + nums[j] == target) {
        
        # Store the pair of indices (1-based)
        result_pairs[[length(result_pairs) + 1]] <- c(i, j)
      }
    }
  }
  
  # Convert the list to a data frame for better readability (optional)
  if (length(result_pairs) > 0) {
    result_df <- do.call(rbind, result_pairs)
    colnames(result_df) <- c("Index1", "Index2")
    return(result_df)
  } else {
    return(NULL)  # Return NULL if no pairs are found
  }
}

# Example usage
nums <- c(1, 2, 3, 4, 5, 6)
target <- 7
result <- two_sum_all_pairs(nums, target)
print(result)

```
```{r}
two_sum <- function(nums, target) {
  # Initialize an empty environment (hashmap) to store indices
  hash_map <- new.env(hash = TRUE, parent = emptyenv())
  result_pairs <- list()
  
  # Iterate through each element in nums
  for (i in seq_along(nums)) {
    complement <- target - nums[i]
    
    # Check if the complement exists in the hash_map
    if (exists(as.character(complement), envir = hash_map)) {
      # Retrieve all indices that match the complement
      indices <- hash_map[[as.character(complement)]]
      
      # Store all pairs found
      for (index in indices) {
        result_pairs[[length(result_pairs) + 1]] <- c(index, i)
      }
    }
    
    # Store the index of the current number in hash_map
    if (!exists(as.character(nums[i]), envir = hash_map)) {
      hash_map[[as.character(nums[i])]] <- c(i)
    } else {
      hash_map[[as.character(nums[i])]] <- c(hash_map[[as.character(nums[i])]], i)
    }
  }
  
  # Convert the list to a data frame for better readability (optional)
  if (length(result_pairs) > 0) {
    result_df <- do.call(rbind, result_pairs)
    colnames(result_df) <- c("Index1", "Index2")
    return(result_df)
  } else {
    return(NULL)  # Return NULL if no pairs are found
  }
}

# Example usage
nums <- c(1, 2, 3, 4, 5, 6)
target <- 7
result <- two_sum(nums, target)
print(result)

```

